---
title: "Homework 1"
author: "Radoslav Hubenov №45708"
date: "12/8/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("MASS", repos = "http://cran.us.r-project.org")
library(MASS)
attach(survey)
library(tidyverse)
```

# Problem 1
## A)
Get the min value of AGE where SEX is "Female".
```{r}
min(survey$Age[survey$Sex == "Female"], na.rm=T)
```
## B)
Sort by height and then get the genders of the three highest.
```{r}
survey$Sex[sort(survey$Height, decreasing=T)][0:3]
```
## V)
Calculate the mean for the ages where Sex is "Male" and Pusle > 80
```{r}
mean(survey$Age[ survey$Sex == "Male" & survey$Pulse > 80], na.rm=T)
```
Split the screen, plot the pie on the first screen and plot the boxplot on the second.
## G)
```{r pressure}
split.screen(c(1,2))
screen(1)
pie(table(survey$Exer))
screen(2)
boxplot(survey$Height)
```

# Problem 2
Not sure how to plot the convergence to infinity of a function.
This gets the values of the function from 1 to 1000, flattens the values into one vector and 
calculates then plots the cummulative mean as n increases to 1000.
```{r}
f <- function(n = 100) {
  count = 0
  for(i in 1:n) {
    xs = sample(1:10, size=3, replace=T)
    
    if((xs[1] + xs[2]) > 2*xs[3]) {
      count = count + 1
    }
  }
  count / n
}

f(100)
f(1000)
f(10000)

map(1:1000, ~f()) %>%
  unlist() %>%
  cummean() %>%
  plot(type="l")

```

# Problem 3


## A)
Calculate the amount of values bigger than 3 and divide by the total count.
```{r}
count = 1000
xs = rnorm(count, mean=4, sd=6)
length(xs[xs > 3]) / 1000
```

## B)
65 percent of xs are under the c and 35 percent are over the c.
```{r}
c = quantile(xs, probs=0.65)
```

## V)
```{r}
m = median(xs)
q1 = median(xs[xs < m])
q3 = median(xs[xs > m])
m
q1
q3
```




